---
format: 
  html: 
    toc: false
    anchor-sections: false
    fig-cap-location: bottom
    tbl-cap-location: top
    number-sections: false
    smooth-scroll: true
    self-contained: true
    output-file: "qmd_output.html"
params:
  data: NA
  excluded: NA
  label: NA
  metaoutcome: NA
  modelranfix: NA
  outcome_measure: NA
  ranking: NA

---

```{r include = FALSE}
library(gt)
```

## MetaInsight Report {.tabset}

### User inputs and selections {.tabset}

#### User selections

```{r echo = FALSE}
if (params$metaoutcome == "Continuous") {outcome_type_txt <- "Continuous (mean difference)"
} else {outcome_type_txt <- "Binary (odds ratio)"}

if (params$outcome_measure == "MD") {outcome_measure_txt <- "Mean difference"
} else if (params$outcome_measure == "SMD") {outcome_measure_txt <- "Standardised mean difference"
} else if (params$outcome_measure == "OR") {outcome_measure_txt <- "Odds ratio"
} else if (params$outcome_measure == "RR") {outcome_measure_txt <- "Risk ratio"
} else if (params$outcome_measure == "RD") {outcome_measure_txt <- "Risk difference"
}

if (params$ranking == "good") {ranking_txt <- "desirable"
} else {ranking_txt <- "undesirable"}

if (params$modelranfix == "random") {modelranfix_txt <- "Random effect"
} else {modelranfix_txt <- "Fixed effect"}

if (is.null(params$excluded)) {excluded_txt <- "None"
} else {excluded_txt <- paste(params$excluded, collapse = ", ")}

```

**Outcome type:** `r outcome_type_txt`

**Outcome measure:** `r outcome_measure_txt`

For treatment rankings, smaller outcome values (e.g. smaller mean values for continuous data, or ORs less than 1 for binary data) are: **`r ranking_txt`**

**Model:** `r modelranfix_txt`

**Studies excluded from sensitivity analysis: ** `r excluded_txt` 

#### Study data 

```{r echo = FALSE}
gt(params$data,
   groupname_col = "group")
```

#### Treatment labels

```{r echo = FALSE}
gt(params$label,
   groupname_col = "group")
```


