---
title: "MetaInsight report"
output: html_document
params:
  bugsnetdt: NA
  data: NA
  excluded: NA
  exclusionbox: NA
  forest: NA
  label: NA
  metaoutcome: NA
  model: NA
  networkstyle: NA
  outcome_measure: NA
  ranking: NA
---

```{r include = FALSE}
library(knitr)

```

### User inputs and selections

**Outcome type**  
Continuous (mean difference) or binary (odds ratio)

```{r}
params$metaoutcome
```

**Study data and treatment labels**

```{r}
params$data

treatment_label(params$label)
```

**Outcome measure**  
Mean difference (MD) or standardised mean difference (SMD) for continuous data  
Odds ratio (OR), risk ratio (RR) or risk difference (RD) for binary data  

```{r}
params$outcome_measure
```

For treatment rankings, smaller outcome values (e.g. smaller mean values for continuous data, or ORs less than 1 for binary data) are desirable (good) or undesirable (bad)

```{r}
params$ranking
```

**Model**  
Random effect (RE) or fixed effect (FE)

```{r}
params$model
```

**Excluded studies**

```{r}
paste(params$excluded, collapse = (", "))
```

### MetaInsight app outputs

**Data used for NMA**

```{r}
knitr::kable(params$data)
```

**Summary of study characteristics**  
Characteristics table of all studies

```{r}
summary_table_plot(params$bugsnetdt, params$metaoutcome)
```

**Summary of study characteristics**  
Characteristics table with studies excluded

```{r}
summary_table_plot(filter(params$bugsnetdt, !Study %in% params$exclusionbox), params$metaoutcome)
```

<!-- **Study results** -->
<!-- Individual study results (for all studies) grouped by treatment comparison -->

<!-- ```{r} -->
<!-- make_netStudy(params$data, params$metaoutcome, params$excluded, params$label, -->
<!--               params$outcome_measure, params$model, params$forest$ForestHeader, -->
<!--               params$forest$ForestTitle)$fplot -->

<!-- ``` -->

<!-- **Network plot** -->
<!-- Network plot of all studies   -->

<!-- Network plot style -->

<!-- ```{r} -->
<!-- params$networkstyle -->
<!-- ``` -->

<!-- Need to fix excluded data -->
<!-- # ```{r} -->
<!-- # make_netgraph(freq_all(params$data, params$metaoutcome, params$label,  -->
<!-- #                        params$outcome_measure, params$model, params$excluded), 1.25) -->
<!-- # ``` -->


