---
title: "MetaInsight report"
output: html_document
params:
  outcome_type: NA
  data: NA
  label: NA
  outcome_measure: NA
  ranking: NA
  model: NA
---

```{r include = FALSE}
library(knitr)

```

### User inputs and selections

**Outcome type**  
Continuous (mean difference) or binary (odds ratio)

```{r}
params$outcome_type
```

**Study data and treatment labels**

```{r}
params$data

treatment_label(params$label)
```

**Outcome measure**  
Mean difference (MD) or standardised mean difference (SMD) for continuous data  
Odds ratio (OR), risk ratio (RR) or risk difference (RD) for binary data  

```{r}
params$outcome_measure
```

For treatment rankings, smaller outcome values (e.g. smaller mean values for continuous data, or ORs less than 1 for binary data) are desirable (good) or undesirable (bad)

```{r}
params$ranking
```

**Model**  
Random effect (RE) or fixed effect (FE)

```{r}
params$model
```

<!-- **Excluded studies** -->

<!-- ```{r} -->
<!-- params$exclusion -->
<!-- ``` -->

### MetaInsight app outputs  

**Data used for NMA** 

```{r}
knitr::kable(params$data)
```

**Summary of study characteristics**
Characteristics table of all studies

```{r}
renderTable({
  bugsnet_sumtb(bugsnetdt(params$data, params$outcome_type, params$label), params$outcome_type)
})
```

**Summary of study characteristics**  
Characteristics table of all studies

```{r}
summary_table_plot(params$data, params$outcome_type, params$label)
```








